Maps

### 2018-01-08 notebooks/031-count-sections.Rmd
Move notebooks into a single directory

---
title: "Number of actual sections"
author: "Lincoln Mullen"
date: "December 2, 2015"
---

@@

```{r}
library("magrittr")
library("readr")
library("dplyr")
library("stringr")
library("knitr")
code_files <- Sys.glob("legal-codes/*")
codes <- lapply(code_files, read_lines)
names(codes) <- code_files %>% basename() %>% str_replace_all("\\.txt", "")
code_info <- read_csv("codes/code-generations.csv")
```

A section is a line with `§` or `SEC.` at the very beginning.

>>>>

---
title: "Count number of sections in corpus"
author: "Lincoln Mullen"
---

@@

```{r}
library("magrittr")
library("readr")
library("dplyr")
library("stringr")
library("knitr")
load("cache/corpus-lsh.rda")
code_files <- Sys.glob("legal-codes/*")
codes <- lapply(code_files, read_lines)
names(codes) <- code_files %>% basename() %>% str_replace_all("\\.txt", "")
code_info <- read_csv("codes/code-generations.csv")
```

The number of sectioned files on disk.

```{r}
Sys.glob("legal-codes-sp")
```

An alternative way of counting. A section is a line with `§` or `SEC.` at the very beginning.

### 2018-01-08 notebooks/101-visualizations-for-article.Rmd
Move notebooks into a single directory

left_join(all_NY1850, NY1850_match_counts, 
          by = c("borrower_section" = "match_section")) %>% 
  select(section = borrower_section, n) %>% 
  mutate(n = ifelse(n < 6, NA, n)) %>% 
  mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% 
  mutate(.,
         column = col_vector(nrow(.), 50),
         row = row_vector(nrow(.), 50)) %>% 
  ggplot(aes(x = column, y = -row, fill = n)) +
  geom_tile(color = "lightgray") +
  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
                    labels = c("6-10", "11-15", "16-20", "21-25", "26-30",
                               "31-35", "36-40", "40+")) +
  labs(x = NULL, y = NULL, fill = "Number of time borrowed") + 
  coord_equal() + 
  theme_minimal() + 
  theme(legend.position = "bottom",
      axis.ticks = element_blank(),
      axis.line = element_blank(), axis.text = element_blank(),
      panel.background = element_blank(), panel.grid = element_blank(),
      legend.key.size = unit(0.5, "cm"),
      plot.margin = unit(c(0, 0, 0, 0), "cm"),
      plot.title = element_text(hjust = 0.5)) +
  ggtitle("Most frequently borrowed sections in NY1850")

>>>>

left_join(all_NY1850, NY1850_match_counts, 
          by = c("borrower_section" = "match_section")) %>% 
  select(section = borrower_section, n) %>% 
  mutate(n = ifelse(n < 6, NA, n)) %>% 
  mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% 
  mutate(.,
         column = col_vector(nrow(.), 50),
         row = row_vector(nrow(.), 50)) %>% 
  ggplot(aes(x = column, y = -row, fill = n)) +
  geom_tile(color = "lightgray") +
  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
                    labels = c("6-10", "11-15", "16-20", "21-25", "26-30",
                               "31-35", "36-40", "40+")) +
  labs(x = NULL, y = NULL, fill = "Number of times borrowed") + 
  coord_equal() + 
  theme_minimal() + 
  theme(legend.position = "bottom",
      axis.ticks = element_blank(),
      axis.line = element_blank(), axis.text = element_blank(),
      panel.background = element_blank(), panel.grid = element_blank(),
      legend.key.size = unit(0.5, "cm"),
      plot.margin = unit(c(0, 0, 0, 0), "cm"),
      plot.title = element_text(hjust = 0.5)) +
  ggtitle("Most frequently borrowed sections in NY1850")

### 2018-01-08 notebooks/102-clustering.Rmd
Move notebooks into a single directory

---
title: "Sparse matrix of comparisons"
author: "Lincoln Mullen"
date: "November 5, 2015"
output: html_document
---

@@

```{r, message=FALSE}
library("Matrix")
library("apcluster")
library("dplyr")
library("readr")
library("textreuse")
source("R/extract-date.R")
source("R/extract_code_names.R")
cache_lsh <- "cache/lsh-sections.rda"
load(file = cache_lsh)
cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
load(file = cache_corpus)
```

@@

```{r}
scores <- section_scores %>% 
  filter(score >= 0.1)
scores
nrow(scores)
```

@@

```{r}
section_names <- lsh_subset(scores)
head(section_names, 10)
length(section_names)
```

@@

```{r}
lookup <- data_frame(section_names, index = 1:length(section_names))
lookup
scores <- scores %>% 
  left_join(lookup, by = c("a" = "section_names")) %>% 
  left_join(lookup, by = c("b" = "section_names")) 
scores
```

@@

```{r}
n <- length(section_names)
m <- sparseMatrix(i = scores$index.x, j = scores$index.y, x = scores$score,
                  dims = c(n, n), symmetric = TRUE)
colnames(m) <- section_names
rownames(m) <- section_names
```

@@

```{r}
write_csv(clusters_df, "out/clusters.csv")
```

@@

```{r, message=FALSE}
dir.create("clusters", showWarnings = FALSE)

>>>>

---
title: "Cluster the documents"
author: "Lincoln Mullen"
date: "November 5, 2015"
output: html_document
---

We are going to create clusters of our documents using the affinity propagration algorithm.

@@

```{r, message=FALSE}
library("Matrix")
library("apcluster")
library("dplyr")
library("readr")
library("textreuse")
source("R/helper.R")
load("cache/corpus-lsh.rda")
```

@@

```{r}
scores_clustering <- scores %>% 
  filter(score >= 0.1)
scores_clustering
nrow(scores_clustering)
```

@@

```{r}
section_names <- lsh_subset(scores_clustering)
head(section_names, 10)
length(section_names)
```

@@

```{r}
lookup <- data_frame(section_names, index = 1:length(section_names))
lookup
scores_clustering <- scores_clustering %>% 
  left_join(lookup, by = c("a" = "section_names")) %>% 
  left_join(lookup, by = c("b" = "section_names")) 
scores_clustering
```

@@

```{r}
n <- length(section_names)
m <- sparseMatrix(i = scores_clustering$index.x,
                  j = scores_clustering$index.y,
                  x = scores_clustering$score,
                  dims = c(n, n), symmetric = TRUE)
colnames(m) <- section_names
rownames(m) <- section_names
```

@@

```{r}
dir.create("out/clusters")
write_csv(clusters_df, "out/clusters/clusters.csv")
```

@@

```{r, message=FALSE}
unlink("clusters", recursive = TRUE)
dir.create("clusters", showWarnings = FALSE)

### 2018-01-08 notebooks/104-network-graphs-in-ggraph.Rmd
Move notebooks into a single directory

```{r}
ggraph(states_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(size = 6, alpha = 0.75, aes(color = region)) +
  geom_node_text(aes(label = name)) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
  scale_color_manual(values = c("South" = "steelblue1",
                                "West" = "coral2",
                                "Atlantic" = "darkgoldenrod2",
                                "New England" = "mediumorchid2",
                                "Midwest" = "palegreen2",
                                "New York" = "peru")) + 
  ggforce::theme_no_axes() +
  labs(title = "State to state borrowings") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```

>>>>

```{r}
set.seed(473)
ggraph(states_g, "igraph", algorithm = "nicely") +
  geom_edge_fan2(aes(edge_width = sections_borrowed, 
                    alpha = 0.9),
                arrow = arrow(type = "open", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  # geom_node_point(size = 6, alpha = 0.15) +
  geom_node_text(aes(label = name), size = 5) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
  scale_color_manual(values = c("South" = "steelblue1",
                                "West" = "coral2",
                                "Atlantic" = "darkgoldenrod2",
                                "New England" = "mediumorchid2",
                                "Midwest" = "palegreen2",
                                "New York" = "peru")) + 
  ggforce::theme_no_axes() +
  labs(title = "State to state borrowings") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```

### 2018-01-08 notebooks/105-most-borrowed-sections.Rmd
Move notebooks into a single directory

most_borrowed <- function(matches_df, matching_code, weighted = FALSE) {
  if (weighted) {
    matches_df <- matches_df %>% 
      group_by(match_section) %>% 
      summarize(score = sum(score, na.rm = TRUE)) %>% 
      mutate(match_code = "All codes",
             score = scales::rescale(score, from = c(0, max(score, na.rm = TRUE)))) %>% 
      rename(borrower_section = match_section)
  } else {
    matches_df <- matches_df %>% 
      group_by(match_section) %>% 
      summarize(n = n()) %>% 
      mutate(match_code = "All codes",
             score = scales::rescale(n, from = c(0, max(n, na.rm = TRUE)))) %>% 
      rename(borrower_section = match_section)
  }

@@

```{r}
borrowings_spectrogram("NY1829")
borrowings_spectrogram("NY1848")
borrowings_spectrogram("MA1836")
borrowings_spectrogram("MD1855")
borrowings_spectrogram("CA1851")

```

>>>>

most_borrowed <- function(matches_df, matching_code, weighted = FALSE) {
  if (weighted) {
    matches_df <- matches_df %>% 
      group_by(match_section) %>% 
      summarize(score = sum(score, na.rm = TRUE)) %>% 
      mutate(match_code = "All codes",
             score = scales::rescale(score, from = c(0, max(score, na.rm = TRUE)))) %>% 
      rename(borrower_section = match_section)
  } else {
    matches_df <- matches_df %>% 
      group_by(match_section) %>% 
      summarize(n = n()) %>% 
      mutate(match_code = "All codes",
             n = ifelse(n == 1, NA, n),
             score = scales::rescale(n, from = c(0, max(n, na.rm = TRUE)))) %>% 
      rename(borrower_section = match_section)
  }

@@

```{r}
borrowings_spectrogram("NY1829")
borrowings_spectrogram("NY1848")
borrowings_spectrogram("MA1836")
borrowings_spectrogram("MD1855")
borrowings_spectrogram("CA1851")
```

### 2018-01-08 notebooks/107-test-values-of-n-k.Rmd
Move notebooks into a single directory

```{r}
valid_params <- comparisons %>% 
  select(-current, -ratio) %>% 
  spread(cf, score) %>% 
  filter(control < 0.02,
         WA > 0.01) 
valid_params %>% 
  arrange(desc(WA))
```

@@

```{r}
comparisons %>% 
  select(-current, -ratio) %>% 
  spread(cf, score) %>% 
  filter(WA > 0.01) %>% 
  ggplot(aes(x = control, label = paste0("n:", n, ",k:", k))) +
  geom_point(aes(y = WA, color = "WA")) +
  geom_point(aes(y = CA, color = "CA")) +
  geom_text_repel(aes(y = WA)) +
  geom_text_repel(aes(y = CA)) +
  labs(title = "Similarity scores for control vs WA and CA for values of n and k",
       x = "Similarity score for control",
       y = "Similarity score for matching section")
```

>>>>

```{r}
valid_params <- comparisons %>% 
  select(-current, -ratio) %>% 
  spread(cf, score) %>% 
  filter(control < 0.02,
         WA >= 0.009) 
valid_params %>% 
  arrange(desc(WA))
```

@@

```{r}
comparisons %>% 
  select(-current, -ratio) %>% 
  spread(cf, score) %>% 
  filter(WA >= 0.009) %>% 
  ggplot(aes(x = control, label = paste0("n:", n, ",k:", k))) +
  geom_point(aes(y = WA, color = "WA")) +
  geom_point(aes(y = CA, color = "CA")) +
  geom_text_repel(aes(y = WA)) +
  geom_text_repel(aes(y = CA)) +
  labs(title = "Similarity scores for control vs WA and CA for values of n and k",
       x = "Similarity score for control",
       y = "Similarity score for matching section")
```

### 2018-01-08 notebooks/108-mapping.Rmd
Move notebooks into a single directory

```{r}
ny_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853")
map_matches <- all_matches %>% 
  filter(xor(borrower_code %in% ny_codes, match_code %in% ny_codes))

map_matches_ny_borrower <- map_matches %>% 
  filter(borrower_code %in% ny_codes) %>% 
  select(-borrower_state) %>% 
  mutate(match_section2 = borrower_section,
         borrower_section2 = match_section) %>% 
  select(-match_section, -borrower_section) %>% 
  rename(borrower_section = borrower_section2, match_section = match_section2) %>%
  select(borrower_section, match_section, score)

map_matches_not_ny <- map_matches %>% 
  filter(!(borrower_code %in% ny_codes)) %>% 
  select(borrower_section, match_section, score)

@@

map_summary <- map_matches %>% 
  filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
  group_by(borrower_state) %>% 
  summarize(score = mean(score)) %>% 
  arrange(desc(score))

@@

ggplot() +
  geom_polygon(data = us_fortified,
               aes(x = long, y = lat, group = group, fill = score),
               color = "black", size = 0.25) +
  scale_fill_manual("Avg. dissimilarity score", values = brewer.pal(5, "YlGn")) +
  coord_map("albers", lat0=30, lat1=40) +
  theme_classic() +
  labs(title = "Strength of borrowings from Field Code (List 2)",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        legend.position = "bottom")
```

>>>>

```{r}
regions <- read_csv("regions.csv")
ny_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853")
ca_codes <- c("CA1850", "CA1851", "CA1858", "CA1868", "CA1872")
ia_codes <- c("IA1851", "IA1859")
mo_codes <- c("MO1849", "MO1856", "MO1879")
ky_codes <- c("KY1851", "KY1854")
oh_codes <- c("OH1853", "OH1879")
searched_for_codes <- oh_codes

map_matches <- all_matches %>% 
  filter(xor(borrower_code %in% searched_for_codes,
             match_code %in% searched_for_codes))

map_matches_ny_borrower <- map_matches %>% 
  filter(borrower_code %in% searched_for_codes) %>% 
  select(-borrower_state) %>% 
  mutate(match_section2 = borrower_section,
         borrower_section2 = match_section) %>% 
  select(-match_section, -borrower_section) %>% 
  rename(borrower_section = borrower_section2, match_section = match_section2) %>%
  select(borrower_section, match_section, score)

map_matches_not_ny <- map_matches %>% 
  filter(!(borrower_code %in% searched_for_codes)) %>% 
  select(borrower_section, match_section, score)

@@

# map_summary <-

  map_matches %>% 
  # filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
  mutate(borrower_code = extract_code_names(borrower_section)) %>% 
  mutate(borrower_state = extract_state(borrower_code)) %>% 
  mutate(borrower_year = extract_date(borrower_year)) %>% 
  filter(score != 0) %>% 
  group_by(borrower_code) %>% 
  summarize(score = mean(score),
            n = n()) %>% 
  arrange(borrower_code) %>% 
  # mutate(state = extract_state(borrower_code)) %>% 
  #   left_join(regions) %>% 
  #   ggplot(aes(x = n, y = score, color = region)) +
  #   geom_point() +
  #   ggtitle("Number of sections borrowed from NY vs average similarity of borrowing")
  write_csv("out/summary-all-codes-with-matches-to-oh.csv")

@@

ggplot() +
  geom_polygon(data = us_fortified,
               aes(x = long, y = lat, group = group, fill = score),
               color = "black", size = 0.25) +
  scale_fill_manual("Avg. similarity score", values = brewer.pal(5, "YlGn")) +
  coord_map("albers", lat0=30, lat1=40) +
  theme_classic() +
  labs(title = "Strength of borrowings from Field Code (All codes)",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        legend.position = "bottom")
```
